---
title: "Code for Adaptive Support Line Simulations and Data Analysis - 2026 update"
output: html_notebook
---

# Helper Functions

### Simulate p-values

```{r}
library(MASS)

freq_simulate_correlated_pvals <- function(m, rho, pi0=0.75) {
  "
  Uses frequentist methadology to simulate m equicorrelated
  p-values with correlation coefficient rho.
  Alternating configuration.
  NOTE: m and m0 (m0 = pi0 * m) should both be multiples of 4
  
  "
  m0 <- pi0 * m
  alt_mu_values <- c(5 * (1:4) / 4)
  rep_count <- (m - m0) / 4
  mu_vec <- c(rep(0, m0), rep(alt_mu_values, rep_count))
  Sigma <- matrix(rho, nrow = m, ncol = m)
  diag(Sigma) <- 1
  Y <- mvrnorm(n = 1, mu = mu_vec, Sigma = Sigma)
  pvals <- pnorm(Y, lower.tail = FALSE)
  return(list(pvals = pvals, is_null = (mu_vec == 0), mu_vals = mu_vec))
}

freq_simulate_pvals <- function(m, pi0=0.75, k=5) {
  "
  Uses frequentist methodology to simulate m independent p-values
  For alternating config: use k=5 and alt_mu_values <- c(k * (1:4) / 4)
  For all-at-5 config: use alt_mu_values <- c(5, 5, 5, 5)
  
  "
  m0 <- pi0 * m
  alt_mu_values <- c(k * (1:4) / 4)
  #alt_mu_values <- c(5, 5, 5, 5)
  rep_count <- (m - m0) / 4
  mu_vec <- c(rep(0, m0), rep(alt_mu_values, rep_count))
  Y <- rnorm(m, mean = mu_vec)
  pvals <- pnorm(Y, lower.tail = FALSE)
  return(list(pvals = pvals, is_null = (mu_vec == 0), mu_vals = mu_vec))
}
```

### Calculate lfdr and bfdr

```{r}
freq_lfdr <- function(pval, is_null) {
  "
  True frequentist bfdr
  
  "
  if (is_null) return(1) else return(0)
}

e_bayes_lfdr <- function(pval, pi0, k = 5) {
  "
  True Bayesian lfdr for alternating configuration.
  Use k=5 to replicate figures from  paper.
  "
  z <- qnorm(1 - pval)
  mu_vals <- k * (1:4) / 4  
  num <- sapply(z, function(z_i) mean(dnorm(z_i - mu_vals)))
  f1 <- num / dnorm(z)
  lfdr <- pi0 / (pi0 + (1 - pi0) * f1)
  return(lfdr)
}

e_bayes_lfdr_all_at_5 <- function(pval, pi0, mu) {
  "
  True Bayesian lfdr for all-at-5 configuration
  Use mu=5 to replicate figures from paper.
  "
  z <- qnorm(1-pval)  
  num <- dnorm(z - mu)   
  denom <- dnorm(z)       
  f1 <- num / denom 
  l <- pi0 / (pi0 + (1 - pi0) * f1)
  return(l)
}

f_hat <- function(pvals, t) {
  "
  grenander estimate of marginal density evaluated
  at t between 0 and 1
  
  "
  p_sorted <- sort(pvals)
  Fm <- ecdf(c(0,pvals))
  g <- grenander(Fm, "decreasing")
  x_knots <- g$x.knots
  f_knots <- g$f.knots
   idx <- findInterval(
    t,
    x_knots,
    left.open = TRUE, 
    all.inside = TRUE
  )

  f_hat <- f_knots[idx]

  return(f_hat)
}


lfdr_est <- function(f_of_p, pi0_hat) {
  "
  estimate lfdr for a single p value using marginal density
  "
  lfdr <- pi0_hat / f_of_p 
  return(lfdr)
}


```

### FDR & bFDR Procedures

```{r}
support_line <- function(pvals, alpha) {
  "
  Support line proceudre at tolerance level alpha
  
  "
  m <- length(pvals)
  p_sorted <- sort(pvals)
  p_ext <- c(0, p_sorted)
  scores <- p_ext - (alpha * 0:m) / m
  k <- which.min(scores) -1
  if (k == 0) return(integer(0))
  threshold <- p_sorted[k]
  return(which(pvals <= threshold))
}

bh <- function(pvals, q = 0.05) {
  "
  Benjamini-Hochberg procedure at tolerance level q
  
  "
  adj <- p.adjust(pvals, method = "BH")
  return(which(adj <= q))
}

storey_support_line <- function(pvals, alpha, lambda = 0.5) {
  "
  Adaptive SL procedure using Storey estimator.
  Differs from standard SL by restricting to p-values
  ≤ lambda and applying SL to the restricted set.
  
  "
  m <- length(pvals)
  pi0_hat <- storey_pi0(pvals, lambda)
  q <- alpha / pi0_hat
  restricted_idx <- which(pvals <= lambda)
  p_restricted <- pvals[restricted_idx]
  m_restricted <- length(p_restricted)
  if (m_restricted == 0) return(integer(0))
  p_sorted <- sort(p_restricted)
  p_ext <- c(0, p_sorted)
  scores <- p_ext - (q * 0:m_restricted / m)
  best_idx <- which.min(scores) - 1
  if (best_idx < 1) return(integer(0))
  threshold <- p_sorted[best_idx]
  return(which((pvals <= threshold) & (pvals <= lambda)))
}

```

### Estimate $\hat \pi_0$

```{r}

lsl_pi0 <- function(pvals) {
  "
  LSL estimator
  
  "
  m <- length(pvals)
  p_sorted <- sort(pvals)
  S <- (1 - p_sorted) / (m + 1 - seq_len(m))
  for (j in 2:m) {
    if (S[j] < S[j - 1]) {
      S_j <- S[j]
      m0_hat <- min(1 / S_j + 1, m)
      return(m0_hat/m)
    }
  }
  return(1)
}

storey_pi0 <- function(p_values, lambda = 0.5) {
  "
  Storey estimator
  
  "
  m <- length(p_values)
  pi0_hat <- (1 + sum(p_values > lambda)) / ((1 - lambda) * m)
  return(pi0_hat)
}

lambda_hat <- function(pvals, q, delta=0.01) {
  "
  Calculate lambda for Adaptive Storey procedure
  as in Gao 2025
  
  "
  m <- length(pvals)
  j_seq <- seq(0, floor((1 - q) / delta), by=1)
  lambda_seq <- j_seq * delta + q 
  l_prev <- storey_pi0(pvals, lambda_seq[1])
  for (i in 2:length(lambda_seq)) {
    lambda_curr <- lambda_seq[i]
    l_curr <- storey_pi0(pvals, lambda_curr)
    # Stopping condition
    if (lambda_curr >= 0.8 || l_curr >= l_prev) {
      return(lambda_curr)
    }
    
    l_prev <- l_curr
  }
  return(lambda_seq[length(lambda_seq)])
}
```

# Numerical Simulations

### FIGURE 3: bFDR vs q (independent p-values)

```{r}
set.seed(123)
library(MASS)
library(ggplot2)
library(dplyr)

"
To generate the plots from the paper, change the alt_mu_values variable
in freq_simulate_pvals function to obtain p-values for either all-at-5
or alternating configurations.
"

m <- 64
N <- 10000
pi0 <- 0.5
q_vals <- seq(0, 0.5, by = 0.1)
procs <- c("SL", "Oracle", "TSSL (q)", "TSSL (q')", "Storey (1/2)", "Storey (q)", "LSL", "AS (0.1)", "AS (0.01)")
results <- matrix(0, nrow = length(q_vals), ncol = length(procs))

for (i in seq_along(q_vals)) {
  q <- q_vals[i]
  proc_res <- matrix(NA, nrow = N, ncol = length(procs))
  
  for (j in 1:N) {
    sim <- freq_simulate_pvals(m, pi0)
    pvals <- sim$pvals
    is_null <- sim$is_null
    m0 <- m * pi0

      ## Procedure 1: SL at level q
      rejs <- support_line(pvals, q)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 1] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 1] <- 0}
      
      ##Procedure 2: Oracle
      rejs <- support_line(pvals, q * m / m0)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 2] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 2] <- 0}
      
      ## Procedure 3: TSSL at level q
      rejs1 <- support_line(pvals, q)
      m0_hat <- m - length(rejs1)
      if (m0_hat == 0) {
        max_idx <- which.max(pvals)
        proc_res[j, 3] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
        }
      else {
        rejs <- support_line(pvals, q * m / m0_hat)
        if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 3] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
        }
        else {proc_res[j, 3] <- 0}
      }
      
      ### Procedure 4: TSSL at level q'
      q_prime <- q / (1+q)
      rejs1 <- support_line(pvals, q_prime)
      m0_hat <- m - length(rejs1)
      if (m0_hat == 0) {
        max_idx <- which.max(pvals)
        proc_res[j, 4] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
        }
      else {
        rejs <- support_line(pvals, q_prime * m / m0_hat)
        if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 4] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
        }
        else {proc_res[j, 4] <- 0}
      }
            
      ## Procedure 5: Storey 1/2
      lambda <- 0.5
      pi0_hat <- storey_pi0(pvals)
      rejs <- storey_support_line(pvals, q)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 5] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 5] <- 0}
      
      ## Procedure 6: Storey q
      lambda <- q
      pi0_hat <- storey_pi0(pvals, lambda)
      rejs <- storey_support_line(pvals, q, lambda)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 6] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 6] <- 0}
    
      ## Procedure 7: LSL
      pi0_hat <- lsl_pi0(pvals)
      rejs <- support_line(pvals, q / pi0_hat)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 7] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 7] <- 0}
      
      ## Procedure 8: AS using delta = 0.1
      lambda <- lambda_hat(pvals, q, 0.1)
      pi0_hat <- storey_pi0(pvals, lambda)
      rejs <- storey_support_line(pvals, q, lambda)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 8] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 8] <- 0}
      
      ## Procedure 9: AS using delta = 0.01
      lambda <- lambda_hat(pvals, q, 0.01)
      pi0_hat <- storey_pi0(pvals, lambda)
      rejs <- storey_support_line(pvals, q, lambda)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 9] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 9] <- 0}
  
  # Store means across 10,000 simulations
  avg_lfdrs <- colMeans(proc_res, na.rm = TRUE)
  results[i, ] <- colMeans(proc_res, na.rm = TRUE)
}
}


# Convert to data frame for plotting
df <- data.frame(
  q = rep(q_vals, each = length(procs)),
  method = factor(rep(procs, times = length(q_vals))),
  lfdr = as.vector(t(results))
)

ggplot(
  df %>% dplyr::filter(!method %in% c("TSSL (q')", "AS (0.01)")),
  aes(x = q, y = lfdr, color = method, linetype = method)
) +
  geom_line(linewidth = 0.9, alpha = 0.8) +  # slightly thinner + transparency
  geom_abline(intercept = 0, slope = 1, linetype = "dotted", color = "black") +
  scale_color_manual(
    values = c(
      "SL" = "#1b9e77",
      "Oracle" = "#d95f02",
      "TSSL (q)" = "#7570b3",
      "Storey (1/2)" = "#e7298a",
      "Storey (q)" = "#66a61e",
      "LSL" = "#e6ab02",
      "AS (0.1)" = "#a6761d"
    )
  ) +
  scale_linetype_manual(
    values = c(
      "SL" = "solid",
      "Oracle" = "dashed",
      "TSSL (q)" = "dotdash",
      "Storey (1/2)" = "longdash",
      "Storey (q)" = "twodash",
      "LSL" = "dotted",
      "AS (0.1)" = "F1"
    )
  ) +
  labs(
    x = "tolerance level q",
    y = "bFDR",
    color = "Procedure",
    linetype = "Procedure"
  ) +
  theme_minimal(base_size = 14) +
  theme(aspect.ratio = 1/1.3) +
  theme(
    aspect.ratio = 1/1.3,
    legend.position = "right",
    legend.key.size = unit(0.4, "cm"),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 11)
  )
```

### FIGURE 4a: bFDR vs $\rho$ (dependent p-values)

```{r}
set.seed(123)
library(MASS)
library(ggplot2)
m <- 64
q <- 0.2
N <- 10000
pi0 <- 0.75
rho_vals <- seq(0, 1, by = 0.1)
procs <- c("SL", "Oracle", "TSSL (q)", "TSSL (q')", "Storey (1/2)", "Storey (q)", "LSL", "AS (0.1)", "AS (0.01)")
num_proc <- length(procs)

results <- matrix(0, nrow = length(rho_vals), ncol = num_proc)

for (i in seq_along(rho_vals)) {
  rho <- rho_vals[i]
  proc_res <- matrix(NA, nrow = N, ncol = num_proc)
  
  for (j in 1:N) {
    sim <- freq_simulate_correlated_pvals(m, rho, pi0)
    pvals <- sim$pvals
    is_null <- sim$is_null
    m0 <- m * pi0

      ## Procedure 1: SL at level q
      rejs <- support_line(pvals, q)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 1] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 1] <- 0}
      
      ##Procedure 2: Oracle
      rejs <- support_line(pvals, q * m / m0)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 2] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 2] <- 0}
      
      ## Procedure 3: TSSL at level q
      rejs1 <- support_line(pvals, q)
      m0_hat <- m - length(rejs1)
      if (m0_hat == 0) {
        max_idx <- which.max(pvals)
        proc_res[j, 3] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
        }
      else {
        rejs <- support_line(pvals, q * m / m0_hat)
        if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 3] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
        }
        else {proc_res[j, 3] <- 0}
      }
      
      ### Procedure 4: TSSL at level q'
      q_prime <- q / (1+q)
      rejs1 <- support_line(pvals, q_prime)
      m0_hat <- m - length(rejs1)
      if (m0_hat == 0) {
        max_idx <- which.max(pvals)
        proc_res[j, 4] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
        }
      else {
        rejs <- support_line(pvals, q_prime * m / m0_hat)
        if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 4] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
        }
        else {proc_res[j, 4] <- 0}
      }
            
      ## Procedure 5: Storey 1/2
      lambda <- 0.5
      pi0_hat <- storey_pi0(pvals)
      rejs <- storey_support_line(pvals, q)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 5] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 5] <- 0}
      
      ## Procedure 6: Storey q
      lambda <- q
      pi0_hat <- storey_pi0(pvals, lambda)
      rejs <- storey_support_line(pvals, q, lambda)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 6] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 6] <- 0}
    
      ## Procedure 7: LSL
      pi0_hat <- lsl_pi0(pvals)
      rejs <- support_line(pvals, q / pi0_hat)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 7] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 7] <- 0}
      
      ## Procedure 8: AS using delta = 0.1
      lambda <- lambda_hat(pvals, q, 0.1)
      pi0_hat <- storey_pi0(pvals, lambda)
      rejs <- storey_support_line(pvals, q, lambda)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 8] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 8] <- 0}
      
      ## Procedure 9: AS using delta = 0.01
      lambda <- lambda_hat(pvals, q, 0.01)
      pi0_hat <- storey_pi0(pvals, lambda)
      rejs <- storey_support_line(pvals, q, lambda)
      if (length(rejs) > 0) {
        max_idx <- rejs[which.max(pvals[rejs])]
        proc_res[j, 9] <- freq_lfdr(pvals[max_idx], is_null[max_idx])
      }
      else {proc_res[j, 9] <- 0}
  
  }

  avg_lfdrs <- colMeans(proc_res, na.rm = TRUE)
  results[i, ] <- colMeans(proc_res, na.rm = TRUE)
}

df <- data.frame(
  rho = rep(rho_vals, each = num_proc),
  method = factor(rep(procs, times = length(rho_vals))),
  lfdr = as.vector(t(results))
)

ggplot(df, aes(x = rho, y = lfdr, color = method)) +  # TRUE for TSSL, FALSE otherwise
  geom_line(size = 1) +
  labs(x = expression(rho),
       y = "bFDR",
       color = "Procedure") +
  theme_minimal(base_size = 14)
```

### FIGURE 4b: Distribution of $\hat \pi_0$ for different values of $\rho$

```{r}
library(ggplot2)
library(dplyr)

set.seed(123)
m <- 64
q <- 0.2
pi0 <- 0.75
N <- 10000

pi0_hat_box_plots <- function(m, q, pi0, N)
{  
  rho_vals <- seq(0, 1, by = 0.25)
  results <- data.frame()
  
  for (rho in rho_vals) {
    for (i in 1:N) {
      sim <- freq_simulate_correlated_pvals(m, rho, pi0)
      pvals <- sim$pvals
  
      # Storey 1/2
      pi0_hat_storey <- storey_pi0(pvals)
      
      # Storey q
      pi0_hat_storey_q <- storey_pi0(pvals, q)
  
      # TSSL
      rejs1 <- support_line(pvals, q)
      m0_hat <- m - length(rejs1)
      pi0_hat_tssl <- m0_hat / m
      
      #AS (0.1)
      lambda <- lambda_hat(pvals, q, 0.1)
      pi0_hat_AS_01 <- storey_pi0(pvals, lambda)
      
      #AS (0.01)
      lambda <- lambda_hat(pvals, q, 0.01)
      pi0_hat_AS_001 <- storey_pi0(pvals, lambda)
      
      #LSL
      pi0_hat_lsl <- lsl_pi0(pvals)
      
      results <- rbind(results,
        data.frame(
          rho = rho,
          pi0_hat = pi0_hat_tssl,
          method = "TSSL (q)"
        ),
        
        data.frame(
          rho = rho,
          pi0_hat = pi0_hat_lsl,
          method = "LSL"
        ),   

        data.frame(
          rho = rho,
          pi0_hat = pi0_hat_AS_01,
          method = "AS (0.1)"
        ),
        
        data.frame(
          rho = rho,
          pi0_hat = pi0_hat_AS_001,
          method = "AS (0.01)"
        ),
        
        data.frame(
          rho = rho,
          pi0_hat = pi0_hat_storey_q,
          method = "Storey (q)"
        ),  
        
        data.frame(
          rho = rho,
          pi0_hat = pi0_hat_storey,
          method = "Storey (1/2)"
        )
      )
    }
  }
  
  results$method <- factor(
    results$method,
    levels = c("AS (0.01)", "AS (0.1)", "LSL", "Storey (1/2)", "Storey (q)", "TSSL (q)")
  )
  return(results)
  }

results <- pi0_hat_box_plots(m, q, pi0, N)
method_colors <- c(
  "AS (0.01)"   = "#F8766D",  
  "AS (0.1)"    = "#D39200",  
  "LSL"         = "#93AA00", 
  "Storey (q)"= "#619CFF",  
  "Storey (1/2)"  = "#00B9E3",  
  "TSSL (q)"    = "#FF00A5"   
)

p <- ggplot(results, aes(x = factor(rho), y = pi0_hat, fill = method)) +
  geom_boxplot(
    outlier.shape = NA,
    coef = 0
  ) +
  scale_fill_manual(values = method_colors, name = "Method") +
  labs(
    x = expression(rho),
    y = expression(hat(pi)[0])
  ) +
  coord_cartesian(ylim = c(0, 1.5)) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text = element_text(size = 16),  
    axis.title = element_text(size = 18), 
  )

print(p)

```

### FIGURE 5: Power comparison table

```{r}
set.seed(123)
library(MASS)
proc_names <- c("SL", "TSSL (q)", "TSSL (q')", "Storey (1/2)", "Storey (q)", "AS (0.01)",  "AS (0.1)", "AS (0.1; 0.5)", "LSL")
num_procs <- length(proc_names)
sim_power <- function(m, pi0, q = 0.2, N = 10000) {
  proc_res <- matrix(0, nrow = N, ncol = num_procs)
  oracle_res <- c()
  for (j in 1:N) {
    sim <- freq_simulate_pvals(m, pi0, k=5)
    pvals <- sim$pvals
    is_null <- sim$is_null
    m0 <- round(pi0 * m)
    m1 <- m - m0
        
    #Oracle
    rejs <- if (m0 == 0) 1:m else support_line(pvals, q * m / m0)
    R1 <- sum(!is_null[rejs])
    oracle_res[j] <- R1 / m1
    
    # Procedure 1: SL at level q
    rejs <- support_line(pvals, q)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 1] <- R1 / m1
    
    #Procedure 2: TSSL at level q
    rejs1 <- support_line(pvals, q)
    m0_hat <- m - length(rejs1)
    rejs <- if (m0_hat == 0) 1:m else support_line(pvals, q * m / m0_hat)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 2] <- R1 / m1
    
    # Procedure 3: TSSL at level q'
    q_prime <- q / (1+q)
    rejs1 <- support_line(pvals, q_prime)
    m0_hat <- m - length(rejs1)
    rejs <- if (m0_hat == 0) 1:m else support_line(pvals, q_prime * m / m0_hat)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 3] <- R1 / m1
    
    # Procedure 4: Storey 1/2
    pi0_hat <- storey_pi0(pvals)
    rejs <- if (m0 == 0) 1:m else storey_support_line(pvals, q)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 4] <- R1 / m1
        
    #Procdure 5: Storey with lambda = q
    pi0_hat <- storey_pi0(pvals, q)
    rejs <- if (m0 == 0) 1:m else storey_support_line(pvals, q, q)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 5] <- R1 / m1
    
    # Procedure 6: AS with delta = 0.01
    lambda <- lambda_hat(pvals, q, 0.01)
    pi0_hat <- storey_pi0(pvals, lambda)
    rejs <- if (m0 == 0) 1:m else storey_support_line(pvals, q, lambda)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 6] <- R1 / m1
    
        
    #Procedure 7: AS with delta = 0.1
    lambda <- lambda_hat(pvals, q, 0.1)
    pi0_hat <- storey_pi0(pvals, lambda)
    rejs <- if (m0 == 0) 1:m else storey_support_line(pvals, q, lambda)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 7] <- R1 / m1
    
    # Procedure 8: AS w/ lambda_hat starting at 0.5 and delta = 0.1
    lambda <- lambda_hat(pvals, 0.5, 0.1)
    pi0_hat <- storey_pi0(pvals, lambda)
    rejs <- if (m0 == 0) 1:m else storey_support_line(pvals, q, lambda)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 8] <- R1 / m1
    
    # Procedure 9: LSL
    pi0_hat <- lsl_pi0(pvals)
    rejs <- if (m0 == 0) 1:m else support_line(pvals, q / pi0_hat)
    R1 <- sum(!is_null[rejs])
    proc_res[j, 9] <- R1 / m1
  }

  avg_power <- colMeans(proc_res)
  rel_power <- avg_power / mean(oracle_res)
  return(rel_power)
}

m_vals <- c(16, 64, 256)
pi0_vals <- c(0.25, 0.5, 0.75)
q <- 0.2
N <- 10000

results <- list()

for (pi0 in pi0_vals) {
  mat <- matrix(NA, nrow = num_procs, ncol = length(m_vals))
  rownames(mat) <- proc_names
  colnames(mat) <- paste0("m", m_vals)
  
  for (mi in seq_along(m_vals)) {
    m <- m_vals[mi]
    mat[, mi] <- sim_power(m, pi0, q, N)
  }
  results[[as.character(pi0)]] <- mat
}

for (pi0 in names(results)) {
  cat("\n=== pi0 =", pi0, "===\n")
  print(round(results[[pi0]], 3))
}
```

### FIGURE 6: Distribution of true and estimated lfdr + distribution of $\hat \pi_0$

```{r}
#| warning: false
#| message: false
set.seed(123)
library(fdrtool)
library(ggplot2)
library(dplyr)
library (patchwork)
library(cowplot)

calc_t_star <- function(q, pi0=0.75, k=5) {
  "
  oracle t* for alternating configuration
  "
  t_vals <- seq(1e-10, 1 - 1e-10, length.out = 10000)
  lfdr_vals <- e_bayes_lfdr(t_vals, pi0)
  idx <- sum(lfdr_vals <= q)
  t_star <- t_vals[idx]
  return(t_star)
}

evaluate_lfdr_at_cutoff <- function(m, pi0, q_grid = seq(0.1, 0.3, by = 0.05), N = 10000) {
  
  results <- data.frame(
    proc = character(),
    type = character(),
    q = numeric(),
    lfdr_value = numeric(),
    pi0_hat = numeric(),
    Oracle_cutoff = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (sim_i in seq_len(N)) {
    sim <- freq_simulate_pvals(m, pi0)
    pvals <- sim$pvals
    is_null <- sim$is_null
    m0 <- round(pi0 * m)
    
    for (q in q_grid) {
      
      pi0_hat_vals <- list() 
      cutoffs <- list()
      
      ## TSSL
      rejs1 <- support_line(pvals, q)
      m0_hat <- m - length(rejs1)
      rejs <- support_line(pvals, q * m / m0_hat)
      if (length(rejs) > 0) cutoffs$TSSL <- rejs[which.max(pvals[rejs])]
      pi0_hat_vals$TSSL <- (m - length(rejs1)) / m
      
      ## Oracle
      rejs <- support_line(pvals, q * m / m0)
      if (length(rejs) > 0) cutoffs$Oracle <- rejs[which.max(pvals[rejs])]
      pi0_hat_vals$Oracle <- m0 / m
      
      ## Storey
      rejs <- storey_support_line(pvals, q)
      if (length(rejs) > 0) cutoffs$Storey <- rejs[which.max(pvals[rejs])]
      pi0_hat_vals$Storey <- storey_pi0(pvals)
      
      ## LSL
      pi0_hat_lsl <- lsl_pi0(pvals)
      rejs <- support_line(pvals, q / pi0_hat_lsl)
      if (length(rejs) > 0) cutoffs$LSL <- rejs[which.max(pvals[rejs])]
      pi0_hat_vals$LSL <- pi0_hat_lsl
      
      ## AS
      lambda <- lambda_hat(pvals, q, 0.1)
      rejs <- storey_support_line(pvals, q, lambda)
      if (length(rejs) > 0) cutoffs$AS <- rejs[which.max(pvals[rejs])]
      pi0_hat_vals$AS <- storey_pi0(pvals, lambda)
      
      t_star <- calc_t_star(q)
      
      for (proc in names(pi0_hat_vals)) {
        pi0_hat_proc <- pi0_hat_vals[[proc]]
        cutoff_idx_proc <- cutoffs[[proc]] 
        if (is.na(pi0_hat_proc) || !is.finite(pi0_hat_proc) || is.null(cutoff_idx_proc)) {
          lfdr_true <- 0
          lfdr_estimated <- 0
        }
        else {
          lfdr_true <- e_bayes_lfdr(pvals[cutoff_idx_proc], pi0)
          lfdr_estimated <- lfdr_est(f_hat(pvals, t_star), pi0_hat_proc)
          lfdr_est_individual_cutoff <- lfdr_est(f_hat(pvals, pvals), pi0_hat_proc)
          }
        results <- rbind(
    results, 
    data.frame(proc = proc, type = "True",
               q = q, lfdr_value = lfdr_true,
               pi0_hat = pi0_hat_proc),
    data.frame(proc = proc, type = "Estimated t*",
               q = q, lfdr_value = lfdr_estimated,
               pi0_hat = pi0_hat_proc),
    data.frame(proc = proc, type = "Estimated individual",
               q = q, lfdr_value = lfdr_est_individual_cutoff,
               pi0_hat = pi0_hat_proc)
  )
      }
    }
  }
  
  return(results)
}


results <- evaluate_lfdr_at_cutoff(
  m = 64,
  pi0 = 0.75,
  q_grid = seq(0.05, 0.3, by = 0.05),
  N = 10000
)

# Split data
true_df <- subset(results, type == "True")
est_df  <- subset(results, type == "Estimated t*")
ind_df <- subset(results, type == "Estimated individual")
# Compute means
true_means <- true_df %>%
  group_by(proc, q) %>%
  summarise(mean_val = mean(lfdr_value), .groups = "drop")

est_means <- est_df %>%
  group_by(proc, q) %>%
  summarise(mean_val = mean(lfdr_value), .groups = "drop")

common_theme <- theme_minimal(base_size = 14) +
  theme(
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 18),
    legend.position = "none"
  )

p1 <- ggplot(true_df, aes(x = factor(q), y = lfdr_value, fill = proc)) +
  geom_boxplot(
    outlier.shape = NA,
    width = 0.7,
    position = position_dodge(width = 0.8),
    coef = 0
  ) +
  stat_summary(
    fun = mean,
    geom = "crossbar",
    width = 0.6,
    color = "white",
    linewidth = 0.4,
    position = position_dodge(width = 0.8)
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  labs(
    x = "Tolerance level (q)",
    y = "True Local FDR",
    fill = "Procedure"
  ) +
  common_theme

p2 <- ggplot(est_df, aes(x = factor(q), y = lfdr_value, fill = proc)) +
  geom_boxplot(
    outlier.shape = NA,
    width = 0.7,
    position = position_dodge(width = 0.8),
    coef = 0
  ) +
  stat_summary(
    fun = mean,
    geom = "crossbar",
    width = 0.6,
    color = "white",
    linewidth = 0.4,
    position = position_dodge(width = 0.8)
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  labs(
    x = "Tolerance level (q)",
    y = "Estimated Local FDR",
    fill = "Procedure"
  ) +
  common_theme

pi0_df <- subset(results, proc != "Oracle")

p3 <- ggplot(pi0_df, aes(x = factor(q), y = pi0_hat, fill = proc)) +
  geom_boxplot(
    outlier.shape = NA,
    width = 0.7,
    position = position_dodge(width = 0.8),
    coef = 0
  ) +
  stat_summary(
    fun = mean,
    geom = "crossbar",
    width = 0.6,
    color = "white",
    linewidth = 0.4,
    position = position_dodge(width = 0.8)
  ) +
  coord_cartesian(ylim = c(0.6, 0.9)) +
  labs(
    x = "Tolerance level (q)",
    y = expression(hat(pi)[0]),
    fill = "Procedure"
  ) +
  common_theme

p4 <- ggplot(ind_df, aes(x = factor(q), y = lfdr_value, fill = proc)) +
  geom_boxplot(
    outlier.shape = NA,
    width = 0.7,
    position = position_dodge(width = 0.8),
    coef = 0
  ) +
  stat_summary(
    fun = mean,
    geom = "crossbar",
    width = 0.6,
    color = "white",
    linewidth = 0.4,
    position = position_dodge(width = 0.8)
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  labs(
    x = "Tolerance level (q)",
    y = "Estimated Local FDR (Individual Cutoffs)",
    fill = "Procedure"
  ) +
  common_theme

legend <- get_legend(
  ggplot(true_df, aes(x = factor(q), y = lfdr_value, fill = proc)) +
    geom_boxplot() +
    labs(fill = "Procedure") +
    theme_minimal(base_size = 14) +
    theme(
      legend.text = element_text(size = 14),
      legend.title = element_text(size = 16)
    )
)

p1
p2
p3
p4
plot(legend)

```

# Meta-data Anlysis

### Load p-values

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
library(fdrtool)
#merten
#pvals <- readRDS("/Users/Sarah/Dropbox/My Mac (sarahms-air.lan)/Downloads/mertens_adjusted_pvals.rds")

#macnamara
pvals <- readRDS("/Users/Sarah/Dropbox/My Mac (sarahms-air.lan)/Downloads/macnamara_pvals.rds")
m <- length(pvals)
```

### FIGURE 7: Histogram

```{r}
ggplot(data.frame(pval = pvals), aes(x = pval)) +
  geom_histogram(binwidth = 0.025, fill = "steelblue", color = "white", boundary = 0) +
  labs(
    title = "p-val histogram",
    x = "p-value",
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14),
    plot.title = element_text(size = 18)
  )
```

### FIGURE 8: FDR across subsets of rejection set

```{r}
library(ggplot2)
library(dplyr)
library(scales)

q <- 0.1
pi0_hat <- storey_pi0(pvals) 
rejs <- bh(pvals, q / pi0_hat)

R <- length(rejs)
sorted_rejs <- rejs[order(pvals[rejs])]
p_sorted <- pvals[sorted_rejs]
first_half_idx  <- 1:floor(R/2)
second_half_idx <- (floor(R/2)+1):R

p_first  <- p_sorted[first_half_idx]
p_second <- p_sorted[second_half_idx]

t_all <- max(p_sorted)
t1 <- max(p_first)
t2 <- max(p_second)

# Expected number of false discoveries
ExpV_all <- m * pi0_hat * t_all
ExpV1    <- m * pi0_hat * t1
ExpV2    <- m * pi0_hat * (t2 - t1)

FDR_all <- ExpV_all / R
FDR_1   <- ExpV1 / max(length(p_first), 1)
FDR_2   <- ExpV2 / max(length(p_second), 1)

df_plot <- data.frame(
  rank = 1:R,
  p = p_sorted
)

# Whole secant line: (0,0) to (R, t_all)
df_sec_all <- data.frame(
  rank = c(0, R),
  p = c(0, t_all),
  group = "0.0914"
)

# First half secant: (0,0) to (R/2, t1)
df_sec_1 <- data.frame(
  rank = c(0, length(p_first)),
  p = c(0, t1),
  group = "0.0386"
)

# Second half secant: (R/2, t1) to (R, t2)
df_sec_2 <- data.frame(
  rank = c(length(p_first), R),
  p = c(t1, t2),
  group = "0.1404"
)

df_secants <- bind_rows(df_sec_all, df_sec_1, df_sec_2)

ggplot() +
  geom_point(data = df_plot, aes(x = rank, y = p), size = 1.3) +
  geom_line(
    data = df_secants,
    aes(x = rank, y = p, color = group),
    linewidth = 1.1
  ) +
  scale_x_continuous(breaks = pretty_breaks(n = 8)) +
  scale_y_continuous(breaks = pretty_breaks(n = 8)) +
  scale_color_discrete(
    labels = function(x) percent(as.numeric(x), accuracy =1)
  ) +
  labs(
    title = "FDR estimates across subsets of rejection set",
    x = "order statistic rank",
    y = "p-value",
    color = "FDR"
  ) +
  theme_bw(base_size = 13) +
  theme(
    plot.title  = element_text(size = 18, face = "plain"),
    axis.title  = element_text(size = 16),
    axis.text   = element_text(size = 14),
    legend.title = element_text(size = 15),
    legend.text  = element_text(size = 14)
  )

```

### FIGURE 9: Callibration

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(fdrtool)
library(knitr)
library(cowplot)
library(grid)
q_vals <- c(0.1, 0.15, 0.2, 0.25, 0.3)
pi0_storey <- storey_pi0(pvals)
pi0_lsl    <- lsl_pi0(pvals)
procedures   <- c("Storey", "LSL")

f_hat_vec  <- f_hat(pvals, pvals)
alpha_vec  <- calibration(pvals)

results_df <- bind_rows(lapply(procedures, function(proc) {
  bind_rows(lapply(q_vals, function(qv) {
    pi0_hat <- if (proc == "Storey") pi0_storey else pi0_lsl

    data.frame(
      pval      = pvals,
      lfdr      = lfdr_est(f_hat_vec, pi0_hat),
      alpha_p   = alpha_vec,
      procedure = proc,
      q         = qv
    )
  }))
}))

compute_cutoff_table <- function(proc_name) {
  df_proc <- results_df %>%
    filter(procedure == proc_name) %>%
    arrange(pval)

  bind_rows(lapply(q_vals, function(qv) {
    df_sub <- df_proc %>% filter(q == qv)
    pi0_q <- if (proc_name == "Storey") pi0_storey else pi0_lsl

    valid_idx <- which(df_sub$lfdr <= qv)
    if (length(valid_idx) == 0) {
      return(data.frame(
        q = qv, cutoff_p_val = NA, p_match = NA,
        LB = NA, UB = NA, pi0_hat_estimate = pi0_q
      ))
    }

    idx <- max(valid_idx)
    lfdr_cut <- df_sub$lfdr[idx]

    match_idx <- which.min(abs(df_sub$lfdr - lfdr_cut))

    data.frame(
      q = qv,
      cutoff_p_val = df_sub$pval[idx],
      p_match      = df_sub$pval[match_idx],
      alpha           = df_sub$alpha_p[match_idx],
      lfdr           = lfdr_cut,
      pi0_hat_estimate = pi0_q
    )
  }))
}

cutoff_tables <- lapply(procedures, compute_cutoff_table)
names(cutoff_tables) <- procedures

cutoff_plot_data <- bind_rows(
  cutoff_tables$Storey %>% mutate(Procedure = "Storey"),
  cutoff_tables$LSL %>% mutate(Procedure = "LSL")
) %>%
  filter(!is.na(cutoff_p_val))

print(kable(cutoff_tables$Storey %>% dplyr::select(q, cutoff_p_val, p_match, alpha, lfdr),
            digits = 4, caption = "Storey Procedure Cutoff Table"))
print(kable(cutoff_tables$LSL %>% dplyr::select(q, cutoff_p_val, p_match, alpha, lfdr),
            digits = 4, caption = "LSL Procedure Cutoff Table"))
results_plot <- results_df %>%
  filter(procedure %in% c("Storey", "LSL"))


p_grid <- seq(min(pvals), max(pvals), length.out = 1000)
f_hat_grid <- f_hat(pvals, p_grid)
lfdr_storey_grid <- lfdr_est(f_hat_grid, pi0_storey)
lfdr_lsl_grid    <- lfdr_est(f_hat_grid, pi0_lsl)
alpha_half_grid   <- calibration(p_grid)
alpha_storey_grid <- calibration_pi0hat(p_grid, pi0_storey)
alpha_lsl_grid    <- calibration_pi0hat(p_grid, pi0_lsl)

# Data for plotting smooth curves
smooth_df <- bind_rows(
  data.frame(p = p_grid, value = lfdr_storey_grid,
             type = "lfdr", procedure = "Storey"),
  data.frame(p = p_grid, value = lfdr_lsl_grid,
             type = "lfdr", procedure = "LSL"),
  data.frame(p = p_grid, value = alpha_storey_grid,
             type = "cal_storey", procedure = "Storey"),
  data.frame(p = p_grid, value = alpha_lsl_grid,
             type = "cal_lsl", procedure = "LSL"),
  data.frame(p = p_grid, value = alpha_half_grid,
             type = "cal_half", procedure = "Half")
)
gg <- ggplot() +

  # lfdr curves (solid)
  geom_line(
    data = smooth_df %>% filter(type == "lfdr"),
    aes(x = p, y = value, color = procedure),
    size = 1,
    show.legend = FALSE
  ) +

  # Calibration lines (dashed)
  geom_line(
    data = smooth_df %>% filter(type == "cal_storey"),
    aes(x = p, y = value, color = "storey_hat"),
    size = 1,
    linetype = "dashed"
  ) +
  geom_line(
    data = smooth_df %>% filter(type == "cal_lsl"),
    aes(x = p, y = value, color = "lsl_hat"),
    size = 1,
    linetype = "dashed"
  ) +
  geom_line(
    data = smooth_df %>% filter(type == "cal_half"),
    aes(x = p, y = value, color = "half"),
    size = 1,
    linetype = "dashed"
  ) +

  # Cutoff lines (nudged if overlapping)
  geom_vline(
    data = cutoff_plot_data %>% filter(Procedure == "Storey"),
    aes(xintercept = cutoff_p_val),
    color = "blue",
    linetype = "dotted",
    size = 1.2,
    alpha = 0.8,
    position = position_nudge(x = -0.0005),
    show.legend = FALSE
  ) +
  geom_vline(
    data = cutoff_plot_data %>% filter(Procedure == "LSL"),
    aes(xintercept = cutoff_p_val),
    color = "red",
    linetype = "dotted",
    size = 1.2,
    alpha = 0.8,
    position = position_nudge(x = 0.0005),
    show.legend = FALSE
  ) +

  # Manual color scale
  scale_color_manual(
    name = "",
    values = c(
      "Storey"     = "blue",
      "LSL"        = "red",
      "storey_hat" = "blue",
      "lsl_hat"    = "red",
      "half"       = "black"
    ),
    breaks = c("lsl_hat", "storey_hat", "half"),
    labels = c(
      expression(hat(pi)[0]~"(LSL)"),
      expression(hat(pi)[0]~"(Storey)"),
      expression(pi[0] == 0.5)
    )
  ) +

  guides(color = guide_legend(ncol = 1)) +

  labs(x = "p-value", y = "local fdr") +

  coord_cartesian(xlim = c(0, 0.2), ylim = c(0, 0.8)) +


  theme_minimal() +
  theme(
    axis.title = element_text(size = 16, color = "black"),
    axis.text  = element_text(size = 14, color = "black"),
    axis.line  = element_line(color = "black"),

    panel.grid.major = element_line(color = "grey80", size = 0.5),
    panel.grid.minor = element_line(color = "grey90", size = 0.3),

    legend.position = "bottom",
    legend.direction = "vertical"
  )


# Extract legend
legend <- cowplot::get_legend(
  gg +
    theme(
      legend.position = "bottom",
      legend.direction = "vertical"
    ) +
    guides(color = guide_legend(ncol = 1))
)

gg_no_legend <- gg + theme(legend.position = "none")


print(gg_no_legend)
grid::grid.newpage()
grid::grid.draw(legend)

```

### TABLE 1: $\hat \pi_0$ estimates

```{r}
q_grid <- c(0.1, 0.2, 0.3)
proc_names <- c("SL", "TSSL (q)", "TSSL (q')", "Storey (1/2)", "Storey (q)", "LSL", "AS_0.01", "AS_0.5_0.1", "AS_0.1")

proc_res <- matrix(0, nrow = length(proc_names), ncol = length(q_grid))
rownames(proc_res) <- proc_names
colnames(proc_res) <- paste0("q=", q_grid)

for (qi in seq_along(q_grid)) {
  q <- q_grid[qi]
  
  # SL at level q
  rejs <- support_line(pvals, q)
  R1 <- length(rejs)
  proc_res["SL", qi] <- 1
  
  # TSSL
  rejs1 <- support_line(pvals, q)
  m0_hat <- m - length(rejs1)
  rejs <- support_line(pvals, q * m / m0_hat)
  R1 <- length(rejs)
  proc_res["TSSL (q)", qi] <- m0_hat / m
  
  #TSSL q'
  q_prime <- q/ (1 + q)
  rejs1 <- support_line(pvals, q_prime)
  m0_hat <- m - length(rejs1)
  rejs <- support_line(pvals, q_prime * m / m0_hat)
  R1 <- length(rejs)
  proc_res["TSSL (q')", qi] <- m0_hat / m
  
  # Storey 1/2
  pi0_hat <- storey_pi0(pvals)
  rejs <- storey_support_line(pvals, q)
  R1 <- length(rejs)
  proc_res["Storey (1/2)", qi] <- pi0_hat
  
  #Storey with lambda = q
  pi0_hat <- storey_pi0(pvals, q)
  rejs <- storey_support_line(pvals, q, q)
  R1 <- length(rejs)
  proc_res["Storey (q)", qi] <- pi0_hat
  
  # Procedure 4: LSL
  pi0_hat <- lsl_pi0(pvals)
  rejs <- support_line(pvals, q / pi0_hat)
  R1 <- length(rejs)
  proc_res["LSL", qi] <- pi0_hat
  
  # Procedure 5: AS with delta = 0.01
  lambda <- lambda_hat(pvals, q, 0.01)
  pi0_hat <- storey_pi0(pvals, lambda)
  rejs <- storey_support_line(pvals, q, lambda)
  R1 <- length(rejs)
  proc_res["AS_0.01", qi] <- pi0_hat
  
  # Procedure 6: AS w/ lambda_hat starting at 0.5 and delta = 0.1
  lambda <- lambda_hat(pvals, 0.5, 0.1)
  pi0_hat <- storey_pi0(pvals, lambda)
  rejs <- storey_support_line(pvals, q, lambda)
  R1 <- length(rejs)
  proc_res["AS_0.5_0.1", qi] <- pi0_hat
  
  #Procedure 7: AS with delta = 0.1
  lambda <- lambda_hat(pvals, q, 0.1)
  pi0_hat <- storey_pi0(pvals, lambda)
  rejs <- storey_support_line(pvals, q, lambda)
  R1 <- length(rejs)
  proc_res["AS_0.1", qi]   <- pi0_hat

}

proc_table <- as.data.frame(proc_res)
proc_table <- round(proc_table, 2)

print(proc_table)
```

### TABLE 2: Number of rejections

```{r}
q_grid <- c(0.1, 0.2, 0.3)
proc_names <- c("SL", "TSSL (q)", "TSSL (q')", "Storey (1/2)", "Storey (q)", "LSL", "AS_0.01", "AS_0.5_0.1", "AS_0.1")

proc_res <- matrix(0, nrow = length(proc_names), ncol = length(q_grid))
rownames(proc_res) <- proc_names
colnames(proc_res) <- paste0("q=", q_grid)

for (qi in seq_along(q_grid)) {
  q <- q_grid[qi]
  
  # SL at level q
  rejs <- support_line(pvals, q)
  R1 <- length(rejs)
  proc_res["SL", qi] <- R1
  
  # TSSL
  rejs1 <- support_line(pvals, q)
  m0_hat <- m - length(rejs1)
  rejs <- support_line(pvals, q * m / m0_hat)
  R1 <- length(rejs)
  proc_res["TSSL (q)", qi] <- R1
  
  #TSSL q'
  q_prime <- q/ (1 + q)
  rejs1 <- support_line(pvals, q_prime)
  m0_hat <- m - length(rejs1)
  rejs <- support_line(pvals, q_prime * m / m0_hat)
  R1 <- length(rejs)
  proc_res["TSSL (q')", qi] <- R1
  
  # Storey 1/2
  pi0_hat <- storey_pi0(pvals)
  rejs <- storey_support_line(pvals, q)
  R1 <- length(rejs)
  proc_res["Storey (1/2)", qi] <- R1
  
  #Storey with lambda = q
  pi0_hat <- storey_pi0(pvals, q)
  rejs <- storey_support_line(pvals, q, q)
  R1 <- length(rejs)
  proc_res["Storey (q)", qi] <- R1
  
  # Procedure 4: LSL
  pi0_hat <- lsl_pi0(pvals)
  rejs <- support_line(pvals, q / pi0_hat)
  R1 <- length(rejs)
  proc_res["LSL", qi] <- R1
  
  # Procedure 5: AS with delta = 0.01
  lambda <- lambda_hat(pvals, q, 0.01)
  pi0_hat <- storey_pi0(pvals, lambda)
  rejs <- storey_support_line(pvals, q, lambda)
  R1 <- length(rejs)
  proc_res["AS_0.01", qi] <- R1
  
  # Procedure 6: AS w/ lambda_hat starting at 0.5 and delta = 0.1
  lambda <- lambda_hat(pvals, 0.5, 0.1)
  pi0_hat <- storey_pi0(pvals, lambda)
  rejs <- storey_support_line(pvals, q, lambda)
  R1 <- length(rejs)
  proc_res["AS_0.5_0.1", qi] <- R1
  
  #Procedure 7: AS with delta = 0.1
  lambda <- lambda_hat(pvals, q, 0.1)
  pi0_hat <- storey_pi0(pvals, lambda)
  rejs <- storey_support_line(pvals, q, lambda)
  R1 <- length(rejs)
  proc_res["AS_0.1", qi]   <- R1

}

proc_table <- as.data.frame(proc_res)
proc_table <- round(proc_table, 2)

print(proc_table)
```

### 
