---
title: "MASL code"
output:
  pdf_document: default
  html_notebook: default
---

The code for the power tables and contour plots utilized the code from the following paper: Solari, A. and Goeman, J.J. (2017), Minimally adaptive BH: A tiny but uniform improvement of the procedure of Benjamini and Hochberg. Biom. J., 59: 776-780. <https://doi.org/10.1002/bimj.201500253>

```{r}
library(mvtnorm)
library(xtable)

alpha = 0.2  
rho = 0

R = matrix(c(1,rho,rho,1),ncol=2)
R1 = matrix(c(1,rho - 1,rho - 1,2 - 2 * rho),ncol=2)
c1 = qnorm(1-alpha)
c2 = qnorm(1 - (alpha/2))


mu1 <- mu2 <- seq(.5,3.5,by=.5) # (mu1,mu2) values
mus = expand.grid(mu1,mu2)
# Compute power to reject both hypotheses for SL and MASL
pow.SL <- pow.MASL <- vector()
for (i in 1:nrow(mus)){
  mu = as.vector(mus[i,], "numeric")
  m1 = mu[1]
  m2 = mu[2]
  
  masl_integrand_1 <- function(z){
    rv <- (pnorm(qnorm(1 - alpha), mean=m2 + rho * (z - m1), sd=sqrt(1 - rho^2)) - 
                    pnorm(qnorm(pnorm(z) - alpha), mean=m2 + rho * (z - m1), sd=sqrt(1 - rho^2))) * 
                   dnorm(z, mean=m1, sd=1)
    return(rv)
    }
  
  masl_integrand_2 <- function(z){
    rv <- (pnorm(qnorm(1 - alpha), mean=m1 + rho * (z - m2), sd=sqrt(1 - rho^2)) - 
                    pnorm(qnorm(pnorm(z) - alpha), mean=m1 + rho * (z - m2), sd=sqrt(1 - rho^2))) * 
                   dnorm(z, mean=m2, sd=1)
    return(rv)
  }
  
  sl_integrand_1 <- function(z){
    rv <- (pnorm(qnorm(pnorm(z) - alpha), mean=m2 + rho * (z - m1), sd=sqrt(1 - rho^2)) - 
                    pnorm(qnorm(1 - alpha/2), mean=m2 + rho * (z - m1), sd=sqrt(1 - rho^2))) * 
                   dnorm(z, mean=m1, sd=1)
    return(rv)
    }
  
  sl_integrand_2 <- function(z){
    rv <- (pnorm(qnorm(pnorm(z) - alpha/2), mean=m1 + rho * (z - m2), sd=sqrt(1 - rho^2)) - 
                    pnorm(qnorm(1 - alpha/2), mean=m1 + rho * (z - m2), sd=sqrt(1 - rho^2))) * 
                   dnorm(z, mean=m2, sd=1)
    return(rv)
  }

  pow.SL[i] = pmvnorm(lower=c(c1,c1), upper=Inf, mean=mu, corr=R)[1] 
  
  pow.MASL[i] = pmvnorm(lower=c(c1,c1), upper=Inf, mean=mu, corr=R)[1] + 
  integrate(masl_integrand_1, lower = c2, upper = Inf, rel.tol = 1e-8)$value +
   integrate(masl_integrand_2, lower = c2, upper = Inf, rel.tol = 1e-8)$value 
}

# Power (%) for rejecting both hypotheses for SL
powmat.SL <- matrix(round(pow.SL*100,0), ncol=length(mu2))
powmat.SL[upper.tri(powmat.SL)]<-""
powmat.SL <- as.data.frame(powmat.SL)
rownames(powmat.SL) <- mu1
names(powmat.SL) <- mu2
print(xtable(powmat.SL, caption = paste("Power (%) for rejecting both hypotheses for SL with correlation = ", rho)))

# Power (%) for rejecting both hypotheses for MASL
powmat.MASL <- matrix(round(pow.MASL*100,0), ncol=length(mu2))
powmat.MASL[upper.tri(powmat.MASL)]<-""
powmat.MASL <- as.data.frame(powmat.MASL)
rownames(powmat.MASL) <- mu1
names(powmat.MASL) <- mu2
print(xtable(powmat.MASL, caption = paste("Power (%) for rejecting both hypotheses for MASL with correlation = ", rho)))

```

Turn table into heatmap

```{r}
library(mvtnorm)
library(tidyverse)

powmat.SL <- matrix(round(pow.SL * 100, 0),
                    nrow = length(mu1),
                    ncol = length(mu2),
                    byrow = FALSE)

powmat.MASL <- matrix(round(pow.MASL * 100, 0),
                      nrow = length(mu1),
                      ncol = length(mu2),
                      byrow = FALSE)

# Keep lower triangle only
powmat.SL[upper.tri(powmat.SL)]     <- NA
powmat.MASL[upper.tri(powmat.MASL)] <- NA

rownames(powmat.SL)   <- mu1
colnames(powmat.SL)   <- mu2
rownames(powmat.MASL) <- mu1
colnames(powmat.MASL) <- mu2

df_SL <- as.data.frame(as.table(powmat.SL))
colnames(df_SL) <- c("mu1","mu2","power")
df_SL$procedure <- "SL"

df_MASL <- as.data.frame(as.table(powmat.MASL))
colnames(df_MASL) <- c("mu1","mu2","power")
df_MASL$procedure <- "MASL"

df_all <- bind_rows(df_SL, df_MASL)

df_all$mu1 <- as.numeric(as.character(df_all$mu1))
df_all$mu2 <- as.numeric(as.character(df_all$mu2))
threshold <- median(df_all$power, na.rm = TRUE)

ggplot(df_all,
       aes(x = factor(mu2),
           y = factor(mu1, levels = rev(sort(unique(mu1)))),
           fill = power)) +
  geom_tile(color = "white") +
  geom_text(aes(
      label = ifelse(is.na(power), "", power),
      color = power < threshold
  ),
  size = 4) +
  facet_wrap(~procedure) +
  scale_fill_viridis_c(option = "C",
                       na.value = "white") +
  scale_color_manual(values = c("black", "white"), guide = "none") +
  theme_minimal(base_size = 15) +
  labs(
    x = expression(mu[2]),
    y = expression(mu[1]),
    fill = "Power (%)"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.text  = element_text(face = "bold")
  )
```

Contour map

```{r}
# Compute power odds ratio of MASL vs SL
powmat.SL <- matrix(pow.SL, ncol=length(mu2))
powmat.MASL <- matrix(pow.MASL, ncol=length(mu2))
powmat.OR <-  powmat.MASL/powmat.SL * (1-powmat.SL)/(1-powmat.MASL)
## ---- Create contour levels ----
levs <- seq(min(powmat.OR),
            max(powmat.OR),
            length.out = 8)

levs <- round(levs, 2)
levs <- unique(levs)

# ---- Colors ----
cols <- viridisLite::viridis(length(levs))

# ---- Square plotting region ----
par(
  mar = c(4,4,2,2),
  pty = "s",
  xaxs = "i",
  yaxs = "i"
)

# ---- Contour plot ----
contour(mu1,
        mu2,
        powmat.OR,
        levels = levs,
        col = cols,
        lwd = 2,
        labcex = 1.6,
        asp = 1,
        method = "edge",
        xlab = expression(mu[1]),
        ylab = expression(mu[2]),
        cex.lab = 1.8,
        cex.axis = 1.4)
```

$\hat \pi_0$ = 1 support line - explicitly calculated bFDR\

$$
Z =
\begin{pmatrix}
Z_1 \\
Z_2
\end{pmatrix}
\sim
N \left(
\begin{pmatrix}
0 \\
0
\end{pmatrix},
\begin{pmatrix}
1 & \rho \\
\rho & 1
\end{pmatrix}
\right)
$$

$$
\text{bFDR} = \mathbb{P}(R > 0) = 1 - \mathbb{P}(R = 0)
$$

$$
\mathbb{P}(R = 0)
=
\mathbb{P}\left(
\arg\min \left\{ p_{(k)} - \frac{\alpha k}{m} \right\} = 0
\right)
$$

$$
=
\mathbb{P}\left(
p_{(1)} > \frac{\alpha}{2}
\;\cap\;
p_{(2)} > \alpha
\right)
$$

$$
=
\mathbb{P}\left(
(p_1 > \tfrac{\alpha}{2},\, p_2 > \tfrac{\alpha}{2})
\;\cap\;
(p_1 > \alpha \;\text{or}\; p_2 > \alpha)
\right)
$$

$$
=
\mathbb{P}\left(
(p_1 > \alpha,\, p_2 > \tfrac{\alpha}{2})
\;\cup\;
(p_1 > \tfrac{\alpha}{2},\, p_2 > \alpha)
\right)
$$

$$
=
\mathbb{P}\left(
Z_1 < \Phi^{-1}(1-\alpha),
\;
Z_2 < \Phi^{-1}(1-\tfrac{\alpha}{2})
\right)
$$

$$
+
\mathbb{P}\left(
Z_1 < \Phi^{-1}(1-\tfrac{\alpha}{2}),
\;
Z_2 < \Phi^{-1}(1-\alpha)
\right)
$$

$$
-\mathbb{P}\left(Z_1 < \Phi^{-1}(1-\alpha),\;Z_2 < \Phi^{-1}(1-\alpha)\right)
$$

```{r}
library(mvtnorm)

# Grid of rho values
rho_vals <- seq(0, 1, by = 0.05)

# q values
q_vals <- c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3)

# Mean vector
mu <- c(0, 0)

# Function to compute bFDR for given rho and q when pi0 = 1
compute_bfdr <- function(rho, q) {
  c1 = qnorm(1-q)
  c2 = qnorm(1 - (q/2))
  
  # correlation matrix
  R = matrix(c(1,rho,rho,1),ncol=2)

  A <- pmvnorm(lower = c(-Inf, -Inf),
               upper = c(c1, c2),
               mean = mu,
               corr = R)[1] +
       pmvnorm(lower = c(-Inf, -Inf),
               upper = c(c2, c1),
               mean = mu,
               corr = R)[1] -
       pmvnorm(lower = c(-Inf, -Inf),
               upper = c(c1, c1),
               mean = mu,
               corr = R)[1]
  
  # bFDR
  bfdr <- 1 - A
  return(bfdr)
}

results <- expand.grid(rho = rho_vals, q = q_vals)

results$bfdr <- mapply(compute_bfdr,
                       rho = results$rho,
                       q   = results$q)

results$q <- factor(results$q)

# Plot
ggplot(results, aes(x = rho, y = bfdr, color = q)) +
  geom_line(size = 1.2) +
  labs(x = expression(rho),
       y = "bFDR",
       color = "q") +
  theme_minimal(base_size = 14)
```

$\pi_0 = 1/2$ SL explicitly calculated bFDR

```{r}
library(mvtnorm)

# Grid of rho values
rho_vals <- seq(0, 1, by = 0.05)

# q values
q_vals <- c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3)

mu2_vals <- c(0.25, 0.5, 1, 2)

# Function to compute bFDR for given rho and q when pi0 = 1
compute_bfdr <- function(rho, q, mu2) {
  mu <- c(0, mu2)
  c1 = qnorm(1-q)
  c2 = qnorm(1 - (q/2))
  
  integrand_1 <- function(z){
  rv <- pnorm(qnorm(pnorm(z) - q/2),
          mean = mu2 + rho * z,
          sd = sqrt(1 - rho^2)) * dnorm(z)
  return(rv)
}
  
  integrand_2 <- function(z) {
    rv <- (1 - pnorm(z, mean = mu2 + rho * z,
          sd = sqrt(1 - rho^2))) * dnorm(z)
    return(rv)
  }
  
  integrand_3 <- function(z){
  rv <- (pnorm(qnorm(pnorm(z) + q/2),
          mean = mu2 + rho * z,
          sd = sqrt(1 - rho^2)) - pnorm(z, mean = mu2 + rho * z, sd = sqrt(1 - rho^2))) * dnorm(z)
  return(rv)
}
  
  # correlation matrix
  R = matrix(c(1,rho,rho,1),ncol=2)

  bfdr <- integrate(integrand_1, lower = c2, upper = Inf, rel.tol = 1e-8)$value + integrate(integrand_2, lower = c2, upper = Inf, rel.tol = 1e-8)$value + integrate(integrand_3, lower = c1, upper = c2, rel.tol = 1e-8)$value
  return(bfdr)
}

results <- expand.grid(rho = rho_vals, q = q_vals, mu2 = mu2_vals)

results$bfdr <- mapply(compute_bfdr,
                       rho = results$rho,
                       q   = results$q,
                       mu2 = results$mu2)

results$q <- factor(results$q)

# Plot with one panel per mu2
ggplot(results, aes(x = rho, y = bfdr, color = q)) +
  geom_line(size = 1.2) +
  facet_wrap(~mu2) +
  labs(x = expression(rho),
       y = "SL bFDR",
       color = "q") +
  theme_minimal(base_size = 14)
```

$\pi_0 = 1/2$ MASL explicitly calculated bFDR

```{r}
library(mvtnorm)

# Grid of rho values
rho_vals <- seq(0, 1, by = 0.05)

# q values
q_vals <- c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3)

mu2_vals <- c(0.25, 0.5, 1, 2)

# Function to compute bFDR for given rho and q when pi0 = 1
compute_bfdr <- function(rho, q, mu2) {
  mu <- c(0, mu2)
  c1 = qnorm(1-q)
  c2 = qnorm(1 - (q/2))
  c3 = qnorm(1 - (3*q/2))
  
  integrand_1 <- function(z){
  rv <- pnorm(qnorm(pnorm(z) - q),
          mean = mu2 + rho * z,
          sd = sqrt(1 - rho^2)) * dnorm(z)
  return(rv)
  }
  
  integrand_2 <- function(z){
  rv <- (1 - pnorm(z, mean = mu2 + rho * z,
          sd = sqrt(1 - rho^2))) * dnorm(z)
  return(rv)
  }
  
  integrand_3 <- function(z){
  rv <- (pnorm(qnorm(pnorm(z) + q),
          mean = mu2 + rho * z,
          sd = sqrt(1 - rho^2)) - pnorm(qnorm(1 - q/2), mean = mu2 + rho * z, sd = sqrt(1 - rho^2))) * dnorm(z)
  return(rv)
}
  
  # correlation matrix
  R = matrix(c(1,rho,rho,1),ncol=2)

  bfdr <- integrate(integrand_1, lower = c2, upper = Inf, rel.tol = 1e-8)$value + integrate(integrand_2, lower = c1, upper = Inf, rel.tol = 1e-8)$value + integrate(integrand_3, lower = c3, upper = c1, rel.tol = 1e-8)$value
  return(bfdr)
}

results <- expand.grid(rho = rho_vals, q = q_vals, mu2 = mu2_vals)

results$bfdr <- mapply(compute_bfdr,
                       rho = results$rho,
                       q   = results$q,
                       mu2 = results$mu2)

results$q <- factor(results$q)

# Plot with one panel per mu2
ggplot(results, aes(x = rho, y = bfdr, color = q)) +
  geom_line(size = 1.2) +
  facet_wrap(~mu2) +
  labs(x = expression(rho),
       y = "MASL bFDR",
       color = "q") +
  theme_minimal(base_size = 14)
```

Functions for simulations

```{r}

simulate_correlated_pvals <- function(mu2, rho) {
  mu_vec <- c(0, mu2)
  Sigma <- matrix(c(1, rho, rho, 1), ncol=2)
  Y <- mvrnorm(n = 1, mu = mu_vec, Sigma = Sigma)
  pvals <- pnorm(Y, lower.tail = FALSE)
  return(list(pvals = pvals, is_null = (mu_vec == 0)))
}

support_line <- function(pvals, alpha) {
  "
  Support line proceudre at tolerance level alpha
  
  "
  m <- length(pvals)
  p_sorted <- sort(pvals)
  p_ext <- c(0, p_sorted)
  scores <- p_ext - (alpha * 0:m) / m
  k <- which.min(scores) -1
  if (k == 0) return(integer(0))
  threshold <- p_sorted[k]
  return(which(pvals <= threshold))
}

masl <- function(pvals, alpha) {
  m <- length(pvals)
  R <- support_line(pvals, alpha)
  if(length(R) == 0) {return(integer(0))}
  else {return(support_line(pvals, alpha * m / (m - 1)))}
}
```

$\pi_0 = 1/2$ MASL simulation

```{r}
library(mvtnorm)
library(ggplot2)
library(MASS)
set.seed(123)


N <- 10000
q_vals <- c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3)
rho_vals <- seq(0, 1, by = 0.1)
mu_vals <- c(0.25, 0.5, 1, 2)
results <- expand.grid(
  rho = rho_vals,
  q = q_vals,
  mu2 = mu_vals
)

results$bfdr <- 0

for (i in 1:nrow(results)) {
  
  rho <- results$rho[i]
  q   <- results$q[i]
  mu2 <- results$mu2[i]
  
  last_null_count <- 0
  
  for (j in 1:N) {
    
    sim <- simulate_correlated_pvals(mu2, rho)
    pvals <- sim$pvals
    is_null <- sim$is_null
    
    R <- masl(pvals, q)
    
    if (length(R) > 0) {
      # last rejection = largest p-value among rejections
      last_rej <- R[which.max(pvals[R])]
      
      if (is_null[last_rej]) {
        last_null_count <- last_null_count + 1
      }
    }
  }
  
  results$bfdr[i] <- last_null_count / N
}

# Plot
ggplot(results, aes(x = rho, y = bfdr, color = factor(q))) +
  geom_line(size = 1) +
  facet_wrap(~ mu2) +
  labs(
    title = "MASL bFDR (simulation)",
    x = expression(rho),
    y = "MASL bFDR",
    color = "q"
  ) +
  theme_minimal()
```

$\hat \pi_0 = 1/2$ SL simulation

```{r}
library(mvtnorm)
library(ggplot2)
library(MASS)
set.seed(123)

N <- 10000
q_vals <- c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3)
rho_vals <- seq(0, 1, by = 0.1)
mu_vals <- c(0.25, 0.5, 1, 2)
results <- expand.grid(
  rho = rho_vals,
  q = q_vals,
  mu2 = mu_vals
)

results$bfdr <- 0

for (i in 1:nrow(results)) {
  
  rho <- results$rho[i]
  q   <- results$q[i]
  mu2 <- results$mu2[i]
  
  last_null_count <- 0
  
  for (j in 1:N) {
    
    sim <- simulate_correlated_pvals(mu2, rho)
    pvals <- sim$pvals
    is_null <- sim$is_null
    
    R <- support_line(pvals, q)
    
    if (length(R) > 0) {
      # last rejection = largest p-value among rejections
      last_rej <- R[which.max(pvals[R])]
      
      if (is_null[last_rej]) {
        last_null_count <- last_null_count + 1
      }
    }
  }
  
  results$bfdr[i] <- last_null_count / N
}

# Plot
ggplot(results, aes(x = rho, y = bfdr, color = factor(q))) +
  geom_line(size = 1) +
  facet_wrap(~ mu2) +
  labs(
    title = "SL bFDR (simulation)",
    x = expression(rho),
    y = "SL bFDR",
    color = "q"
  ) +
  theme_minimal()
```
